### 2014-10-24 Implementations.tex
Added Screenshots
Revised Threats.
Added short description of Implementation.

\textbf{Consent}\\
I have read and understood the above privacy policy and agree that my data is collected and processed accordingly.

\end{verbatim}
\end{quote}

@@

\subsection{Privacy Dashboard}
\subsection{Transfer Encryption (HTTPS/SSL)}
\subsection{Database Access Policies}

\subsection{Anonymization of recorded trips}
- remove precise date information, only day of week.

\subsection{Randomization of GPS data}

>>>>

\textbf{Consent}\\
I have read and understood the above privacy policy and agree that my data is collected and processed accordingly.
\end{quote}

@@

Reporting to Data Protection Authority (Bundesamt für Datenschutz)?

\subsection{Privacy Dashboard}
TODO: Add description of dashboard. With relation to 7C's of Privacy.

\begin{figure}
\includegraphics[width=\textwidth]{screenshots/login.png}
\caption{Live+Gov Privacy Dashboard Login}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{screenshots/recordings.png}
\caption{Live+Gov Privacy Dashboard Recording Overview}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{screenshots/raw.png}
\caption{Live+Gov Privacy Dashboard Raw Data View}
\end{figure}

\begin{figure}
\includegraphics[width=\textwidth]{screenshots/processed.png}
\caption{Live+Gov Privacy Dashboard Processed Data View}
\end{figure}

\subsection{Transfer Encryption (HTTPS/SSL)}
\begin{figure}
\includegraphics[width=\textwidth]{screenshots/HTTPS.png}
\caption{HTTPS connection to Privacy Dashboard}
\end{figure}

\subsection{Database Access Policies}
Access rules for data controller and processor.
Data Processing Journal.
Python script for deletion of data when it is older than a given date.

\subsection{Anonymization of trips}
Privacy by Design: We do never collect name and email address in our DB.
Python script that deletes user information from trip.
% Python script that reomves precise date information, only day of week.

\subsection{K-Anonymity of GPS routes}
Python script that deletes all parts of journeys that have are not near to at least k other journeys.

TODO: Insert Literature Reference.
TODO: Add screenshots.

\subsection{Randomization of GPS data}
Python Script that adds random noise to GPS data.
